### 2023-04-03 reachable-resilience.tex
up

The characterization is used to show that Petri nets are $\post^*$-effective.

@@

\begin{proof}
Let us show that Reset VASS, that are WSTSs with strong upward compatibility, don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow \post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable 
%in counter $i$ 
by examining if there is %some vector $v$ in the basis such that $v(i)=0$
$0$ in the basis%
. But reachability of $0$  %in a counter $i$ 
is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
%	$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\end{proof}

@@

The authors from \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
have only been concerned with the case $\Safe = \uparrow \Safe$
and $\Bad =\downarrow \Bad$, however as mentioned in Section~3
the property for instance of mutual exclusion is often modelised with $\Safe = \downarrow \Safe$.
Hence it makes sense to consider this symmetrical case as well. \\

>>>>

The characterization is used to show that Petri nets are $\post^*$-effective. Since the downward reachability problem is decidable for Petri-nets, we deduce the following:

@@

\begin{proof}
Let us show that Reset VASS, that are WSTSs with strong upward compatibility, don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one is able to compute a finite basis of $\uparrow \post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable 
%in counter $i$ 
by examining if there is %some vector $v$ in the basis such that $v(i)=0$
$0$ in the basis%
. But reachability of $0$  %in a counter $i$ 
is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
%	$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\end{proof}

@@

The authors from \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
have only been concerned with the case $\Safe = \uparrow \Safe$
and $\Bad =\downarrow \Bad$, 
\mathieu{pas tout à fait vrai: dans le technical report \cite{DBLP:conf/gg/Ozkan22} il considère aussi le cas où Bad et Safe sont tous les deux clos par le haut mais aussi le cas Safe clos par le bas Bad clos par le haut.}
 however as mentioned in Section~3
the property for instance of mutual exclusion is often modelised with $\Safe = \downarrow \Safe$.
Hence it makes sense to consider this symmetrical case as well. \\

\mathieu{rappeler résultats de \cite{DBLP:conf/gg/Ozkan22}}

\begin{theorem}{\cite{DBLP:conf/gg/Ozkan22}}
The bounded-state-resilience problem is decidable for \textcolor{red}{fin-marked} 
strongly compatible WSTS
 which are 
 {\em \textcolor{red}{lossy} } 
 and 
 {\em \textcolor{red}{$\bot$-bounded}  }
 if $\Bad = \uparrow \Bad$ and $\Safe = \downarrow \Safe$.
\end{theorem}
